\documentclass[marginmode, 11pt]{res}

\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{geometry}

\usepackage[autostyle=false, style=english]{csquotes}
\MakeOuterQuote{"}
\setmainfont{Adobe Caslon Pro}
\setlist{parsep=0pt, leftmargin=15pt}
\geometry{a4paper, left=22mm, top=35mm}
\setlength\parskip{12pt}
\newsectionwidth{90pt}
\newcommand{\centered}[1]{\moveleft.48\hoffset\centerline{#1}}

\begin{document}

\centered{\LARGE\textbf{Olivier Blanvillain}}
% \centered{54 Scrutton Street}
% \centered{London EC2A 4PH}
% \centered{+417 86 85 77 85}
\centered{\texttt{olivier.blanvillain@gmail.com}}
\vspace{12pt}

\begin{resume}

\section{Education}

2022:~ PhD in Computer Science at EPFL

2015:~ EPFL Master's degree in Computer Science

2012:~ EPFL Bachelor's degree in Computer Science

\section{Experience}

2023--present:~ Software Engineer at Hudson River Trading (London)

\begin{itemize}
  \item Use C++ and Python to implement platforms and tools for algorithmic trading;
  \item Develop scalable data storage and distribution systems for statistical analysis.
\end{itemize}

2016--2022:~ Doctoral Assistant at EPFL in the Programming Methods Laboratory under the supervision of Prof. Martin Odersky (Lausanne, 5.5 years)

\begin{itemize}
  \item Active member of the Scala 3 compiler team;
  \item Co-designed, implemented and formalized a new language feature: match types;
  \item Teaching assistant for Functional Programming and Parallelism \& Concurrency.
\end{itemize}

2015--2016:~ Software Engineer at MFG Labs (Paris, 15 months)

\begin{itemize}
  \item Developed an Adtech product using Scala, PostgreSQL, Spark, Elasticsearch, AWS.
\end{itemize}

2013:~ Software Engineer Intern at CERN (Geneva, 6 months)

\section{Publications}

O. Blanvillain. "Type-Safe Regular Expressions". In \emph{Scala Symposium}, 2022 (SCALA'22)

O. Blanvillain, J. Brachthäuser, M. Kjaer, M. Odersky. "Type-Level Programming with Match Types". In \emph{Symposium on Principles of Programming Languages}, 2022 (POPL'22)

M. Odersky, O. Blanvillain, F. Liu, A. Biboudis, H. Miller, S. Stucki. "Simplicitly: Foundations and Applications of Implicit Function Types". In \emph{Symposium on Principles of Programming Languages}, 2018 (POPL'18)

O. Blanvillain, N. Kasioumis, V. Banos. "BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs". In \emph{Proceedings of the 4th International Conference on Web Intelligence, Mining and Semantics}, 2014 (WIMS'14).

\section{Personal}

Born on July 9, 1990, dual French-Swiss citizenship.

Languages: French (mother tongue), English (fluent), Spanish (B2).

Hobbies: Music (piano, drums and lots of listening), board games, cycling.

\end{resume}

\end{document}
